---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# legiscanrr

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of legiscanrr is to provide tools in R to easily interact with the [LegiScan API](https://legiscan.com/legiscan). You can use the API to retrieve information about legislations in US states and Congress, such as bill details, sponsors, full bill texts, roll call records and more. 

This package contains two main groups of functions:

* Wrapper functions for LegiScan APi operations to retrieve information from LegiScan API.
    * API key from LegiScan is required. Register for a key [here](https://legiscan.com/legiscan)
* Data processing functions to parse information such as bill metadata, bill sponsor, roll call votes, from the JSON files retrieved via API or [direct download](https://legiscan.com/datasets)
    * See [documentation page](articles/parse-json.html) for more details on the types of information we can extract.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("fanghuiz/legiscanrr")
```

## Example

```{r example}
library(legiscanrr)
```

Get bill details via API using `get_bill()`

```{r}
bill_example <- get_bill(bill_id = 230086)

head(bill_example)
```

Extract bill metadata using `parse_bill()`

```{r}
bill_meta <- parse_bill(bill_example)

str(bill_meta)
```

Extract bill progress information using `parse_bill_progress()`

```{r}
parse_bill_progress(bill_example)
```

Extract information about sponsors for this bill using `parse_bill_sponsor()`

```{r}
sponsor <- parse_bill_sponsor(bill_example)

str(sponsor)
```

