---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# legiscanrr

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of legiscanrr is to provide tools in R to easily interact with the [LegiScan API](https://legiscan.com/legiscan). You can use the API to retrieve information about legislations in US states and Congress, such as bill details, sponsors, full bill texts, roll call records and more. 

Two main groups of functions:

* wrapper functions for LegiScan APi operations to xxx
* data processing functions to parse JSON files downloaded locally

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("fanghuiz/legiscanrr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(legiscanrr)
## basic example code
```


## To do 

