---
title: "Retrieve bill full text"
# date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Retrieve bill full text}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE
)
```


```{r}
library(legiscanrr)
```


## From API

Find the identifier for bill text document `doc_id` we want to retrieve and pass it to `get_bill_text()`. We will get back a list containing details about the text document, with the element `doc` containing the document itself in base64 encoding.

```{r}
doc_1877162 <- get_bill_text(doc_id = 1877162)

doc_1877162
```

To retrieve the text from the base64 encoded document, we pass this list to `decode_bill_text()`. This will 1) transform the input list into a data frame, and 2) attach the decoded text as an additional column `text_docoded`.

```{r}
text_decode_1 <- decode_bill_text(doc_1877162)
str(text_decode_1)
```

Decoded text looks like this:

```{r results='asis'}
text_decode_1$text_decoded
```


## From local json

If we have saved the API response from `get_bill_text()` in json format locally, we can decode the text by passing in the paths to the .json files. 

If we save the files under sub-directory `text`, then we can use `find_json_path()` to help us with the search.

```{r}
text_paths <- find_json_path(base_dir = "../inst/extdata", file_type = "text")

text_paths
```

Then pass the file path directly to `decode_bill_text()`, which will perform the importing and decoding accordingly. 

```{r}
text_decode_2 <- decode_bill_text(text_paths[3])
str(text_decode_2)
```

```{r results='asis'}
text_decode_2$text_decoded
```

